Mahotas: Open source software for scriptable computer vision

### 2012-08-08 paper.tex
TXT I just added wavelets to mahotas
ENH Less meaningless details, more meaningful ones

The interface is a procedural interface, with most functions working
independently of each other (there is code sharing at the implementation
level).

\begin{description}
\item[features] Some feature descriptors. In particular, Haralick texture
features, Zernike moments, local binary patterns, threshold adjacency
statistics.
\item[morphological functions] Erosion and dilation, as well as some more
complex operations.
\item[watershed] seeded watershed.
\item[thresholding] some thresholding methods.
\item[polygon operations] convex hull, polygon drawing.
\item[\textsc{surf}] Speeded-up Robust Features.
\end{description}

@@

When meaningful, a structuring element is used to define neighbourhoods or
adjacency relationships (some functions which use this concept are: watershed,
erosion, and median filtering). Generally, the default is to use a $3 \times 3$
cross as the default if no structuring filter is given (the exception to this
rule is the median filter, where the default is a $3 \times 3$ square).

@@

These functions normally contain a lot of boiler-plate code: read the
arguments, perform some sanity checks, perhaps a bit of initialisation, and
then, the switch on the input type with the help of the
\code{HANDLE\_INTEGER\_TYPES()}, \code{HANDLE\_FLOAT\_TYPE()}, and
\code{HANDLE\_TYPES()} macros, which call the right specialisation of the
template that does the actual work. In this example \code{erode} implements
(binary) erosion:

@@

Most of the functions follow this architecture.

@@

Mahotas includes a full test suite. Every function has at least one
corresponding test case. There are no known bugs.

It has been available in the Python Package Index since April~2010 and has been
downloaded over 20,000~times\footnote{This does not include any downloads from
other sources.}.

>>>>

The interface is a procedural interface, with most functions working
independently of each other (there is code sharing at the implementation
level, but this is hidden from the user).

The main functionality is grouped into the following categories:

\begin{description}
\item[\textsc{surf}] Speeded-up Robust Features.
\item[Wavelet] Haar and Daubechies wavelets.
\item[features] Some feature descriptors. In particular, Haralick texture
features, Zernike moments, local binary patterns, threshold adjacency
statistics.
\item[morphological functions] Erosion and dilation, as well as some more
complex operations.
\item[watershed] seeded watershed.
\item[polygon operations] convex hull, polygon drawing.
\end{description}

@@

When meaningful, a structuring element is used to define neighbourhoods or
adjacency relationships (morphological functions, in particular, use this
convention). Generally, the default is to use a $3 \times 3$ cross as the
default if no structuring filter is given (the exception to this rule is the
median filter, where the default is a $3 \times 3$ square).

@@

This functions retrieves the arguments, performs some sanity checks, performs a
bit of initialisation, and finally, switches in the input type with the help of
the \code{HANDLE\_INTEGER\_TYPES()} macro, which call the right specialisation
of the template that does the actual work. In this example \code{erode}
implements (binary) erosion:

@@

@@

Python is an ideal language for fast development of both applications and
scientific software. With a fast library of computer vision and image
processing functions (implemented in \cpp{}, as the standard Python interpreter
is too slow for a direct Python implementation).

Mahotas has been available in the Python Package Index since April~2010 and has
been downloaded over 20,000~times. This does not include any downloads from
other sources. Mahotas includes a full test suite (version 1.0 has 100\% test
coverage). There are no known bugs.
